---
title: "plot"
author: "Courtney Chan"
date: "October 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Problem 2 plots for HW 4

##Loading the necessary libraries.

```{r loading packages}
library(tidyverse)
library(viridis)

library(p8105.datasets)

library(plotly)
```

Preliminary steps to clean the data and recode the variable names of day of the week.

```{r naming dataset and values}

instacart = janitor::clean_names(instacart) %>% mutate(order_dow = recode(order_dow, `0` = "Sunday", `1` = "Monday", `2` = "Tuesday", `3` = "Wednesday", `4` = "Thursday", `5` = "Friday", `6` = "Saturday")) %>% 
  mutate(order_dow = forcats::fct_relevel(order_dow, c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))) %>%
  rename(hour = order_hour_of_day)

```

Since the original datset is too large, I am taking a sample of 5000 observations.

```{r taking a sample of the original data}

samp_instacart = 
  instacart %>% 
  sample_n(5000)

```

##Creating a line graph

Using our sample of 5000, I created a line graph, plotting the hour of the day and number of orders received. 

```{r line graph}

samp_instacart %>%
  group_by(hour) %>%
  summarize(orders = n()) %>% plot_ly(x = ~hour, y = ~orders, type = "scatter", mode = "lines",
          alpha = 0.5)

```

Looking at this plot, as the day goes on, the number of orders greatly increases. The number of orders start to rise at about hour 6, with a sharp increase to peak orders of approximately 400 around 11. From there, the number of orders declines, dropping off more sharply at hour 17.

